Patterns in Knowledge Production in Sweden and Finland, 1640–1828

### 2016-11-17 inst/examples/20161117-manuscript.Rmd
ok

---
title: "Digital History in Finland, 1488-1828"
author: "Leo Lahti, Jani Marjanen, Hege Roivainen, Mikko Tolonen"
date: date: "`r Sys.Date()`"
output: markdown_document
---

@@

# Remove very early and late years
dfo <- dfo %>% filter(publication_year > 1400 & publication_year < 1911)

>>>>

---
title: "Patterns in Knowledge Production in Sweden and Finland, 1640–1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: date: "`r Sys.Date()`"
output: markdown_document
---

@@

# Analysis time window
dfo <- dfo %>% filter(publication_year >= 1640 & publication_year <= 1828)
